systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-19 paper/trunk/systemfit_estimation.tex
added reference to Zellner & Theil (1962) in the paragraph about 3SLS estimation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@616 591db2bd-e0a0-4d22-8c19-2192dbb7da31

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case the GLS is generally called °Seemingly Unrelated Regression°
(SUR) (see \citealp{zellner62}). 
Note, while an unbiased OLS or WLS estimation requires only that 
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( E \left[ u_i | X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( E \left[ u | X \right] = 0 )$.

@@

If the regressors are correlated with the disturbances 
($E \left( u | X \right) \neq 0$) and 
the disturbances are contemporaneously correlated, 
a Generalized Least Squares (GLS) version of the two-stage least squares
estimation leads to consistent and efficient estimates.
This estimation procedure is generally called °Three-stage Least
Squares° (3SLS).

>>>>

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case the GLS is generally called °Seemingly Unrelated Regression°
(SUR) \citep{zellner62}.
Note, while an unbiased OLS or WLS estimation requires only that 
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( E \left[ u_i | X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( E \left[ u | X \right] = 0 )$.

@@

If the regressors are correlated with the disturbances 
($E \left( u | X \right) \neq 0$) and 
the disturbances are contemporaneously correlated, 
a Generalized Least Squares (GLS) version of the two-stage least squares
estimation leads to consistent and efficient estimates.
This estimation procedure is generally called °Three-stage Least
Squares° (3SLS) \citep{zellner62b}.
